Unsupervised learning of Gaussian mixture models in linear time using a variational Bayesian method

### 2017-05-17 articles/nips-2017/ms.tex
god that's shit

\section{Search strategy}

>>>>

The mixing weights follow a multinomial distribution.  For this reason,
although the weights of future mixtures are not known, it can be shown that
the sum of the log of $K$ weights follow the function,
\begin{equation}
  \sum_{k=1}^{K+\Delta{K}}\log\weight_k\future \approx -K\log{K} + g_0
  \label{eq:g}
\end{equation}

\noindent{}such that if the integration constant $g_0$ is known, Eq. \ref{eq:g}
provides an upper bound on the possible contribution to the message length
(maximum entropy).  In practice we store the values of $K$ and 
$\sum_{k=1}^{K}\log\weight_k$ for optimized mixtures, and update our estimate
of the integration constant when predicting the message length of future
mixtures.  Depending on the distribution of the data, the sum of the log of
the weights can have a value lower than $-K\log{K} + g_0$, but the same
functional form will be followed.  For this reason, we fit the approximating
function,
\begin{equation}
G(K) = -Kg_1\log{K} + g_0 \approx \sum_{k=1}^{K+\Delta{K}}\log\weight_k 
\end{equation}

\noindent{}using the stored values of $\{K,\sum_{k=1}^{K}\log\weight_k\}$ from
previously optimized mixtures.  These two linear fitting routines provide an
estimate of the expectation, the variance, \emph{and} an upper bound on the
sum of the log of the weights of unobserved mixtures.

There is no equivalent function we can derive for the log-likelihood of future
mixtures, or the sum of the log of the determinants.  
% Li and Barron
The change in the log-likelihood and the determinant of the covariance
matrices will depend on the data.
% Li and Barron
One could suppose that the determinants of the covariance matrices will on
average decrease with additional components, but to our knowledge there is 
no theoretical basis for the functional form.
Lacking a grounded theoretical basis for these two functions, we collate them
into a single term and approximate it with a second-order polynomial function,
$H(K)$,
\begin{equation}
H(K) = h_2K^2 + h_1K + h_0 \approx -\sum_{n=1}^{N}\log\sum_{k=1}^{K+\Delta{K}}\weight_{k}f_{k}(\data_n|\vecmean_k,\veccov_k)\future - \frac{D+2}{2}\sum_{k=1}^{K + \Delta{K}}\log|\veccov_k|\future \quad .
\end{equation}

% FIt and determine a variance.

Given the functions $G(K)$ and $H(K)$, we update our estimates of the 
coefficients $\vec{g}$ and $\vec{h}$ after any proposed mixture has been
optimized (Section \ref{sec:search-strategy}).  While $G(K)$ is an analytic
function, $H(K)$ is merely adopted for simplicity.  A more grounded
approximation is welcomed.  However, in Section \ref{sec:experimental-results}
we show that our $H(K)$ approximation is sufficient, even with a simplistic
search strategy.

\section{Search strategy}
\label{sec:search-strategy}
